### 2014-02-04 trunk/ feature-selection-high-recall/FeatureSelectionProject/doc/fs_hr/empirical.tex

In this section, we conduct experiments to study the feature selection
performances of several well known methods such as Symmetrical
Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Information Gain Rank
(IGR), Correlation Based Rank (CBR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, 
Correlation-based Feature Subset Selection (CFS)~\cite{Hall1998}, 
Reliff (R)~\cite{Robnik-Sikonja2003} , mRMR~\cite{peng2005} and our proposed 
methods: High Recall Expectation (HRE) and High Recall Log likelihood (HRL), 
High Precision Expectation (HPE), High Precision Log likelihood (HPL). 
The first five methods are variable rank methods and the last seven
are subset rank methods.  {\bf TODO Rodrigo: explain variable rank
and subset rank first.}

>>>>

In this section, we conduct experiments to study the feature selection
performances of several well known methods such as Symmetrical
Uncertainty Rank (SUR), Gain Ratio Rank (GRR), Information Gain Rank
(IGR), Correlation Based Rank (CBR), Conditional Entropy Rank (CER)~\cite{guyon_jmlr03}, 
Correlation-based Feature Subset Selection (CFS)~\cite{Hall1998}, 
Reliff (R)~\cite{Robnik-Sikonja2003} , mRMR~\cite{peng2005} and our proposed 
methods: High Recall Expectation (HRE) and High Recall Log likelihood (HRL), 
High Precision Expectation (HPE), High Precision Log likelihood (HPL). 
The first five methods are variable rank methods and the last seven
are subset rank methods. The first five methods are variable rank methods that select variables by ranking them with some metric and the last seven are subset rank methods that assess subsets of variables and consider previous selections to decide the next selection.
